### 2016-05-05 lineups.Rnw
shape and size of JTT example

set.seed(12345)
ggplot(data = jTT, aes(from_id = from, to_id = to)) + 
  geom_net(aes(shape = as.factor(group)), directed = T, label = T, labelcolour='blue',vjust = -1, hjust =2, arrowgap = .05, colour = 'black') + 
  theme_net() + theme(legend.position = "none")
@

>>>>

set.seed(12345) 
ggplot(data = jTT, aes(from_id = from, to_id = to)) + 
  geom_net(aes(shape = as.factor(group)), directed = T, label = T, labelcolour='grey80',vjust = 0, hjust =0, arrowgap = .15, colour = 'black', size=10) + 
  expand_limits(x=c(-0.1,1.1), y=c(-0.1,1.1)) +
  theme_net() +
  theme(legend.position = "none")
@
